---
title: "gt Table"
author: "Matt Bixley"
date: "22/09/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

## gt

[Exploring the gt (Grammar Of Tables) Package in R](https://towardsdatascience.com/exploring-the-gt-grammar-of-tables-package-in-r-7fff9d0b40cd)

```{r gt}
if(!require("gt")) install.packages("gt")
library(gt)
```

Make a basic table
```{r table1}
t1 <- penguins %>% 
  tibble() %>% 
  filter(species == "Adelie") %>% 
  group_by(island, year) %>% 
  summarise_if(is.numeric, sum) %>% 
  mutate(island = case_when(
    island == "Biscoe" ~ "Biscoe Island",
    island == "Dream" ~ "Dream Island",
    island == "Torgersen" ~ "Torgersen Island"
  )) %>% 
    gt(rowname_col = "year")
t1
```

```{r colvars}
colvars <- c("bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g")
```

Add a summary row
```{r table2}
t2 <- t1 %>%
  summary_rows(
    groups = T,
    columns = vars(colvars),
    fns = list(AVERAGE = "mean"),
    formatter = fmt_number,
    use_seps = T,
    decimals = 0
  )
t2

```

headers and footers
colvars <- c("bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g")
```{r table3}
t3 <- t2 %>% 
  cols_label(
    bill_length_mm = "Bill Length",
    bill_depth_mm = "Bill Depth",
    flipper_length_mm = "Flipper Length",
    body_mass_g = "Body Mass"
    ) %>% 
  tab_header(title = "All About Adelie Penguins",
    subtitle = "Yearly measurements of penguin things") %>% 
  cols_align(align = "right", columns = T) %>% 
  tab_footnote(
    footnote = "In grams",
    location = cells_column_labels(
      columns = vars(body_mass_g)
    )
  ) %>% 
  tab_footnote(
    footnote = "In mm",
    location = cells_column_labels(
      columns = vars(bill_length_mm, bill_depth_mm, flipper_length_mm)
    )
  )
t3
```

